The Psychology of Online Political Hostility -- How Aggressiveness of People Effects Their Online and Offline Comment Towards Political Incidents

### 2024-02-14 main_folder/paper/The Psychology of Online Political Hostility.qmd
add a graph, changed some comments

---
title: "The Psychology of Online Political Hostility -- How Aggressiveness of People Effects Their Online and Offline Comment Towards Political Incidents"
author: 
  - Yiyi Feng, Yingxvan Sun
date: February 13, 2024
date-format: long
format:
  pdf:
    toc: true
    number-sections: true
thanks: "Code and data are available at: https://github.com/kqlqkqlqF/The-Psychology-of-Online-Political-Hostility.git. This paper is replicated from paper the Psychology of Online Political Hostility -- A Comprehensive, Cross-National Test of the Mismatch Hypothesis, available at : https://doi.org/10.1017/S0003055421000885."
abstract: "In contemporary society, the widespread influence of the internet and electronic technology has made the online world an indispensable part of daily human life. However, amidst this digitalization, a significant challenge has emerged: the proliferation of hostile online discussion environments. This phenomenon has sparked a fundamental inquiry: why do online interactions consistently exhibit greater hostility than offline communication? What is the relationship between this trend and individuals' inherent aggressiveness? This paper aims to replicate and analyze data from existing studies investigating the statistical disparities in individual behavior during online and offline political discussions. Additionally, it employs secondary research to explore how individuals' levels of aggressiveness correlate with the observed differences in online and offline political discourse."
bibliography: referencespaper2.bib
---

@@

#### Preamble ####
# Purpose: Writing a paper titled "The Psychology of Online Political Hostility -- How Aggressiveness of People Effects Their Online and Offline Comment Towards Political Incidents"
# Author: Yiyi Feng, Yingxvan Sun
# Date: Febraury 12, 2024
# Contact: yiyi.feng@mail.utoronto.ca, lindayx.sun@mail.utoronto.ca

####Workspace setup ####
library(tidyverse)
library(janitor)
library(knitr)
library(ggplot2)
library(kableExtra)

@@

raw_data_dk <-
  read_csv(
    file = "../data/analysis_data/combined_cleaned_data_dk.csv",
    show_col_types = FALSE)
```

@@

[^1]: Rstudio [@citeR] was used for producing the code and this paper. A series of R packages were used: [@gg2], [@knitr], [@kable], [@janet], and [@tidy].

@@

#### Calculate the mean value for US and DK Online and Offline Hostile Score####
us_mean_on <- mean(raw_data_us$hostile_online)
us_mean_off <- mean(raw_data_us$hostile_offline)
dk_mean_on <- mean(raw_data_dk$hostile_online)
dk_mean_off <- mean(raw_data_dk$hostile_offline)
#add all of the values into a tibble
mean_table <- tibble(
  Category = c("US_ON", "US_OFF", "DK_ON", "DK_OFF"),
  Mean = c(us_mean_on, us_mean_off, dk_mean_on, dk_mean_off)
)
#make a table
kable(mean_table)
```

@@

@@

Our analysis reveals a positive correlation between individuals' levels of aggression and the degree of hostility they exhibit in both online and offline political discussions. This suggests that individuals with higher aggression tend to display more pronounced political hostility regardless of the medium. While the original paper focused on the impact of status-driven risk-taking on online versus offline hostility, finding a positive correlation, our study extends this understanding by demonstrating that the dimension of aggression plays a similar role, highlighting the significant influence of personal traits on political hostility in both platforms.

Contrary to our initial hypothesis that individuals with aggressive personalities would exhibit more different behaviors in online versus offline political discussions, our data did not show a correlation between aggression levels and the difference in hostility between these two contexts. This finding diverges from our expectations and suggests that, despite the increased anonymity and lack of accountability online, aggression does not significantly alter the perceived severity of political conflicts between online and offline environments. This is in line with the original paper's suggestion that political conflicts are not perceived to be more severe online than offline, indicating that individuals with aggressive traits do not differ markedly from average participants in their perception of hostility severity across these platforms.

In summary, our replication study reveals that individual aggressiveness correlates with increased political hostility, uniformly affecting both online and offline discussions. Crucially, it also indicates that there is not a significant correlation between aggression levels and the difference in hostility between these two contexts even for the more aggressive Internet users. This finding challenges the premise that digital environments inherently amplify political antagonism, instead highlighting the overarching role of inherent personal traits in dictating the tone of political discourse, irrespective of the medium.

@@

This study has room for improvement.

@@

# Appendix

>>>>

---
title: "The Psychology of Online Political Hostility -- How Aggressiveness of People Effects Their Online and Offline Comment Towards Political Incidents"
author: 
  - Yiyi Feng, Yingxvan Sun
date: February 13, 2024
date-format: long
format:
  pdf:
    toc: true
    number-sections: true
thanks: "Code and data are available at: https://github.com/kqlqkqlqF/The-Psychology-of-Online-Political-Hostility.git. This paper is replicated from paper the Psychology of Online Political Hostility -- A Comprehensive, Cross-National Test of the Mismatch Hypothesis, available at : https://doi.org/10.1017/S0003055421000885."
abstract: "In contemporary society, the widespread influence of the internet and electronic technology has made the online world an indispensable part of daily human life. However, amidst this digitalization, a significant challenge has emerged: the proliferation of hostile online discussion environments.  This paper aims to replicate and analyze data from existing studies investigating the statistical disparities in individual behavior during online and offline political discussions. Additionally, it employs secondary research to explore how individuals' levels of aggressiveness correlate with the observed differences in online and offline political discourse. Our findings indicate that there is no substantial variance in hostility levels between online and offline political discussions, irrespective of an individual's level of aggression."
bibliography: referencespaper2.bib
---

@@

#### Preamble ####
# Purpose: Writing a paper titled "The Psychology of Online Political Hostility -- How Aggressiveness of People Effects Their Online and Offline Comment Towards Political Incidents"
# Author: Yiyi Feng, Yingxvan Sun
# Date: Febraury 12, 2024
# Contact: yiyi.feng@mail.utoronto.ca, lindayx.sun@mail.utoronto.ca
####Workspace setup ####
library(tidyverse)
library(janitor)
library(knitr)
library(ggplot2)
library(kableExtra)
library(patchwork)
if (!require("pacman")) install.packages("pacman")
pacman::p_load("stargazer", "here", "gridExtra", "weights", "tidyverse",
               "jtools", "clubSandwich", "lm.beta")

@@

raw_data_dk <-
  read_csv(
    file = "../data/analysis_data/combined_cleaned_data_dk.csv",
    show_col_types = FALSE)

df.us <- readRDS(here("main_folder/data/raw_data", "s1_us_2018.rds"))

df.dk <- readRDS(here("main_folder/data/raw_data", "s2_dk_2019.rds"))

df.us2 <- readRDS(here("main_folder/data/raw_data", "s3_us_2019.rds"))

df.us3.part <- readRDS(here("main_folder/data/raw_data", "s4_us_2021.rds"))  %>% 
  filter(part_online > 0 & part_offline > 0)

```

@@

[^1]: Rstudio [@citeR] was used for producing the code and this paper. A series of R packages were used: [@gg2], [@knitr], [@kable], [@janet], [@pac], [@patch], [@test] and [@tidy].

@@

#### Calculate the mean value for US and DK Online and Offline Hostile Score####
us_mean_on <- mean(raw_data_us$hostile_online)
us_mean_off <- mean(raw_data_us$hostile_offline)
dk_mean_on <- mean(raw_data_dk$hostile_online)
dk_mean_off <- mean(raw_data_dk$hostile_offline)
#add all of the values into a tibble
mean_table <- tibble(
  Category = c("US-ON", "US-OFF", "DK-ON", "DK-OFF"),
  Mean = c(us_mean_on, us_mean_off, dk_mean_on, dk_mean_off)
)
#make a table
kable(mean_table)
```

@@

```{r}
#| label: fig-half
#| fig-cap: Distribution of Perceived Negativity of Online and Offline Discussions in the United States and Denmark 
#| echo: false
#| message: false
#| warning: false

# US plot
p1.us <- df.us %>%  
  select(tone_offline_neg, tone_online_neg) %>% 
  gather(environment, value, 1:2) %>% 
  mutate(environment = factor(environment, levels = c("tone_online_neg", "tone_offline_neg"), labels = c("Online", "Offline"))) %>% 
  ggplot(aes(x = value, fill = environment)) + 
  geom_density(alpha = 0.6) + 
  xlab("") + 
  ylab("Density") + 
  scale_fill_grey(guide = FALSE) + 
  ggtitle("A. USA") +
  theme_bw()

# DK plot
p1.dk <- df.dk %>%  
  select(tone_offline_neg, tone_online_neg) %>% 
  gather(environment, value, 1:2) %>% 
  mutate(environment = factor(environment, levels = c("tone_online_neg", "tone_offline_neg"), labels = c("Online", "Offline"))) %>% 
  ggplot(aes(x = value, fill = environment)) + 
  geom_density(alpha = 0.6) + 
  xlab("") + 
  ylab("") + 
  scale_fill_grey(name = NULL) + 
  ggtitle("B. Denmark") +
  theme_bw()

# Combine plots using patchwork
p1 <- p1.us + p1.dk + plot_layout(ncol = 2)

# Print combined plot
p1
```

In (@fig-half), the negativity of online (dark gray) and offline (light gray)
discussions were demonstrated. Although there's no statistically significant difference between hostile levels in online and offline political discussions, we can still see that in both countries, offline discussions have low negativity compared with online discussions. Similarly, there are more online discussions with a higher negativity. As a result, we can still conclude there's a general trend of people being more hostile in online political discussions, although the statistical test doesn't support this idea.

@@

In the original study, the authors delved into the influence of status-driven risk-taking behavior on hostility, both online and offline, uncovering a positive correlation. Building upon this groundwork, our aim was to shed further light on the role of aggressiveness while emphasizing the intricate relationship between individual traits and political hostility across different communication mediums. Leveraging insights from pertinent psychological literature, we posited that there exists a positive correlation between an individual's level of aggressiveness and the intensity of hostility exhibited in their online and offline political exchanges.

However, contrary to our initial hypothesis, our empirical findings did not reveal a significant correlation between aggressiveness and the disparities in hostility observed across online and offline environments. This unexpected result challenges the conventional belief that heightened aggressiveness would lead to a discernible escalation in the severity of political conflicts, particularly in the context of online interactions characterized by increased anonymity and diminished accountability.

Furthermore, our study yielded a conclusion consistent with the original paper, indicating that the perceived severity of political conflicts online does not necessarily surpass that of offline discussions. Additionally, individuals with aggressive tendencies did not demonstrate a statistically significant difference in their perception of hostility on these digital platforms compared to non-aggressive participants.

In summary, our replication study contributes to the growing understanding of the dynamics between individual aggressiveness and political hostility, highlighting their influence on discussions across both online and offline arenas. Importantly, it underscores the nuanced nature of these relationships, suggesting that even among more aggressive internet users, the impact of aggressiveness on the divergence in hostility between online and offline environments may not be statistically significant. This nuanced perspective challenges the notion that digital platforms inherently exacerbate political confrontations, emphasizing instead the pivotal role of inherent individual traits in shaping the discourse tone, irrespective of the communication medium.

@@

@@

\newpage
# Appendix
